DeepSphere: a graph-based spherical CNN

### 2019-09-19 main.tex
fix latex

Neural networks (NNs) have proved to be great tools to solve inference problems. % when a huge amount of data is available.
As such, multiple kinds of NNs have been developed to handle spherical data, each with their strengths and weaknesses.
% balance of ??
% Exploit the geometrical properties of the domain, symmetries.
% desiderata or tradeoff
We identified the following desiderata for a spherical NN.
\begin{enumerate}
	\item \textbf{Respect the domain.}
		By respecting the domain, a spherical NN should respect the symmetries of the sphere, i.e., be equivariant to rotation, and not deform the sphere, e.g., by a projection on the icosahedron.
	\item \textbf{Be powerful.}
	\item \textbf{Scale.}
	\item \textbf{Be flexible.}
\begin{enumerate}
* powerful / generality $\Rightarrow$ isotropic vs anisotropic\\
* scale: computational cost \& memory usage (feature maps)\\
* flexible (samplings, irregular), simplicity (implementation)\\

>>>>

Neural networks (NNs) have proved to be great tools to solve inference problems. % when a huge amount of data is available.
As such, multiple kinds of NNs have been developed to handle spherical data, each with their strengths and weaknesses.
% balance of ??
% Exploit the geometrical properties of the domain, symmetries.
% desiderata or tradeoff
We identified the following desiderata for a spherical NN.
\begin{enumerate}
	\item \textbf{Respect the domain.}
		By respecting the domain, a spherical NN should respect the symmetries of the sphere, i.e., be equivariant to rotation, and not deform the sphere, e.g., by a projection on the icosahedron.
	\item \textbf{Be powerful.}
	\item \textbf{Scale.}
	\item \textbf{Be flexible.}
\end{enumerate}
* powerful / generality $\Rightarrow$ isotropic vs anisotropic\\
* scale: computational cost \& memory usage (feature maps)\\
* flexible (samplings, irregular), simplicity (implementation)\\
